\section{Literature Review}

\subsection{Overview}
This chapter presents a critical review of the literature concerning online assessment systems, with a particular focus on their evolution during and after the COVID-19 pandemic. The section establishes the theoretical and empirical foundation for the Veritas Online Assessment system by exploring trends, challenges, and innovations in online proctoring, integrity assurance, and AI-driven automated essay scoring (AES) and feedback generation. Particular emphasis is placed on recent advancements in natural language processing (NLP) and large language models (LLMs), which have significantly influenced modern digital assessment practices \citep{Topuz2022,Hussein2020}.

\subsection{Study Related Works}

\citet{Topuz2022} conducted a systematic review of 22 online assessment systems to identify emerging trends in online measurement and evaluation during the Emergency Remote Teaching (ERT) period. Their findings emphasized three major features: multi-platform compatibility, enhanced security through biometric authentication, and automated proctoring. Commercial systems such as Examity, ProctorU, and Safe Exam Browser were highlighted for their multimodal authentication mechanisms, integrating webcam monitoring, keystroke analysis, and facial recognition.

Complementing this work, \citet{Kurniati2023} investigated challenges faced by Indonesian teachers across multiple educational levels. Their study identified infrastructure limitations, increased academic dishonesty, and inconsistent student discipline as key obstacles. To mitigate these challenges, teachers adopted adaptive strategies such as shifting from objective to subjective assessments and implementing localized solutions, including home visits and shared mobile phone access.

Subsequent studies have expanded upon these foundational findings. \citet{Hussein2020} evaluated several commercial online proctoring tools and identified cost, accessibility, and ethical concerns as significant barriers to adoption. Similarly, \citet{Arno2021} conducted a comprehensive feature-based comparison of 29 commercial proctoring systems, concluding that hybrid approaches—combining automated facial detection with human supervision—provided an optimal balance between exam integrity and user experience. In addition, \citet{JiaHe2021} proposed an Intelligent Online Proctoring System (IOPS) that employed artificial intelligence for facial, eye, and voice monitoring, demonstrating a measurable reduction in cheating incidents during real university examinations.

Guidelines for effective online assessment during emergency remote teaching were further articulated by \citet{Rahim2020}, who emphasized the importance of aligning assessment methods with learning objectives and prioritizing formative evaluation. More recent work by \citet{Ali2025} examined phased implementations of remote online examinations in undergraduate medical education, revealing that preparatory mock exams and small-group training sessions significantly improved student confidence and satisfaction despite persistent technological constraints.

Building on advancements in assessment integrity and proctoring technologies, recent literature has increasingly explored Automated Essay Scoring (AES) and Automated Short Answer Grading (ASAG) using large language models (LLMs). These approaches aim to improve grading efficiency for subjective assessments while addressing scalability challenges inherent in manual evaluation during ERT periods. \citet{MizumotoEguchi2023} demonstrated the effectiveness of GPT-3 for AES on TOEFL essays, achieving substantial agreement with human raters (Quadratic Weighted Kappa of approximately 0.7) through zero-shot prompting, while also enabling immediate feedback on linguistic and content-related traits. Similarly, \citet{Schneider2024} applied GPT-4 for ASAG tasks and reported reliable scoring performance on rubric-based educational benchmarks, particularly for short-answer questions requiring concept listing.

Further investigations by \citet{Mansour2024} evaluated the performance of LLMs such as GPT-3.5 and LLaMA in essay proficiency scoring, highlighting their capability to generate trait-based feedback related to coherence and relevance, albeit with varying levels of correlation to human evaluators. In parallel, \citet{Kundu2024} analyzed the use of ChatGPT and LLaMA across multiple AES datasets, noting their effectiveness as grading assistants while cautioning against their tendency toward harsher evaluation of nuanced responses. Collectively, these findings underscore the growing potential of LLM-assisted assessment systems when integrated within human-in-the-loop evaluation frameworks.

\subsection{Identifying Milestones of Related Literature and Finding the Gaps}

\subsubsection{Milestones}

\begin{itemize}
\item \textbf{Phase 1: Manual Online Assessments (Pre-2020)}
    \begin{itemize}
        \item Early online assessment systems primarily focused on basic digital exam delivery and security mechanisms. \citet{FosterLayman2013} compared eight online proctoring systems, analyzing features such as authentication methods, webcam-based monitoring, browser lockdown tools, and associated security risks. Their study demonstrated that webcam-based monitoring served as a significant deterrent to cheating. Building on this work, \citet{KarimShukur2016} examined authentication techniques in online examinations and proposed a preference-based classification model, grouping methods into knowledge-based, possession-based, biometric, and contextual authentication approaches.
        \item \textbf{Strength:} Provided clear conceptual frameworks for understanding the design and security mechanisms of early online assessment systems.
        \item \textbf{Limitation:} The studies were largely descriptive, with limited real-world deployment and testing, and placed minimal emphasis on scalability or suitability for low-bandwidth and resource-constrained environments.
    \end{itemize}

\item \textbf{Phase 2: Emergency Remote Teaching (2020–2021)}
    \begin{itemize}
        \item The COVID-19 pandemic forced the rapid adoption of online examinations, exposing significant challenges in assessment integrity. \citet{Topuz2022} reviewed online assessment systems used during this period, identifying common features such as desktop-focused platforms, pre-exam facial recognition, semi-automatic monitoring, and integration with learning management systems (e.g., Moodle). Additional studies compared commercial proctoring tools in terms of scalability, authentication mechanisms, and monitoring capabilities.
        \item \textbf{Strength:} Provides a timely and comprehensive overview of solutions developed in response to pandemic-driven challenges.
        \item \textbf{Limitation:} Relies primarily on self-reported data and largely overlooks infrastructure constraints, particularly in developing regions.
    \end{itemize}


\item \textbf{Phase 3: AI and Automation Integration (2021–2024)}
    \begin{itemize}
        \item Machine learning techniques have enabled automated cheating detection in online assessments. \citet{JiaHe2021} developed an AI-based proctoring system capable of real-time monitoring, while \citet{TiongLee2021} applied deep learning to detect abnormal candidate behavior and unusual network patterns. Review studies indicated that these systems improved detection accuracy, although issues with false positives were noted.
        \item \textbf{Strength:} Represents a shift toward proactive, automated enforcement of assessment integrity.
        \item \textbf{Limitation:} Relies on high-quality data and stable internet connections, with limited attention to bias, fairness, and privacy concerns.
    \end{itemize}

\item \textbf{Phase 4: User-Centric Design and Ethics (2024–2025)}
    \begin{itemize}
        \item Recent research emphasizes ethics, privacy, and user experience in online assessment systems. Studies highlight reduced video surveillance, GDPR compliance, hybrid assessment models, and the continued importance of human oversight in AI-based proctoring systems \citep{Rahim2020, Ali2025, Arno2021}. Equity and bias considerations across diverse student populations are increasingly emphasized.
        \item \textbf{Strength:} Stronger focus on ethical, legal, and human-centered design principles.
        \item \textbf{Limitation:} Research is still in early stages, with limited empirical evidence and largely Western-centric perspectives.
    \end{itemize}

\item \sloppypar \textbf{Phase 5: LLM-Driven Automated Scoring for Essays and Short Answers (2023–2026)}
    \begin{itemize}
        \item This phase focuses on integrating large language models (LLMs) such as GPT-3, GPT-4, ChatGPT, and Llama for Automated Essay Scoring (AES) and Automated Short Answer Grading (ASAG), emphasizing rubric-based evaluation, feedback generation, and human-AI collaboration. Key milestones include \citet{MizumotoEguchi2023}, who demonstrated GPT-3's potential for AES on TOEFL essays with high human agreement (QWK $\sim$0.7) via zero-shot prompting; \citet{Schneider2024}, who applied GPT-4 for ASAG, achieving reliable scoring on short textual responses; \citet{Mansour2024}, evaluating LLMs for proficiency essay scoring with trait-based feedback; \citet{Kundu2024}, finding LLMs harsher and less correlated with humans in AES but useful as assistants; and \citet{Xiao2024}, proposing a dual-process human-AI framework for AES that improves efficiency and reduces misgrading through collaborative workflows.
        \item \textbf{Strength:} Advances scalability and personalization in online assessments by leveraging LLMs for consistent, instant scoring and detailed feedback, enabling efficient handling of large-scale subjective responses (e.g., essays and short answers) with high agreement to human raters (QWK 0.68–0.88 across studies). Promotes accessibility through open-source models and prompting techniques, reducing educator workload while supporting diverse formats like rubric-based exam questions.
        \item \textbf{Limitation:} LLM performance remains sensitive to prompt design and training biases, leading to inconsistencies in domain-specific or non-English contexts. Studies show variable human-LLM correlations and potential over-harshness or leniency, with limited empirical validation in real-world, resource-constrained environments, raising concerns about reliability without human oversight.
    \end{itemize}

\end{itemize}

\subsubsection{Gaps Identified}

Despite significant advancements, several critical gaps remain.

\begin{enumerate}
    \item \textbf{Poor Accessibility for Students with Disabilities} 
        \begin{itemize}
            \item A significant but often overlooked limitation in online assessment systems is their lack of accessibility for students with disabilities. \citet{Topuz2022} identified that most existing platforms employ restrictive security measures, such as forced browser lockdowns, hidden taskbars, and required software installations—that unintentionally exclude users who depend on assistive technologies like screen readers or adaptive input devices. These constraints prevent such students from navigating exams independently and raise ethical concerns about inclusivity.
            \item \citet{Hussein2020} also observed that advanced proctoring systems rarely incorporate Universal Design for Learning (UDL) principles, focusing instead on surveillance and integrity rather than equitable usability. Similarly, \citet{Rahim2020} highlighted that during emergency remote teaching, accessibility and fairness were underemphasized, especially for learners with sensory or cognitive disabilities. \citet{UcaGunes2024} further confirmed that accessibility policies were inconsistent across institutions, and few systems offered accommodations such as extended time or alternative input modes. Collectively, these studies demonstrate a persistent design bias, prioritizing security and standardization over inclusivity.
        \end{itemize}
    


    \item \textbf{The ``Security vs. Connectivity” Gap} 
        \begin{itemize}
            \item A persistent limitation in online assessment research lies in the trade-off between exam security and network reliability. Most secure proctoring platforms depend on continuous high-speed internet and uninterrupted video streaming to verify student behavior. However, studies in developing regions reveal that weak digital infrastructure severely impedes assessment validity. \citet{Kurniati2023} found that Indonesian teachers frequently abandoned video-based testing due to poor bandwidth and device incompatibility. Similarly, \citet{Ali2025} reported that 57\% of medical students in Pakistan experienced internet instability during live-proctored exams, resulting in high anxiety and incomplete submissions. \citet{Hussein2020} further noted that commercial proctoring tools such as ProctorU and Respondus required intensive data streaming and high computing power, creating inequity between students with and without robust connections. \citet{Topuz2022} confirmed that even secure systems like Safe Exam Browser remain dependent on real-time connectivity. Hence, despite advances in digital invigilation, current systems lack adaptive, low-bandwidth monitoring mechanisms capable of maintaining integrity under unstable network conditions. Addressing this limitation is crucial for equitable implementation of online assessments in bandwidth-constrained environments such as Ethiopia.
        \end{itemize}
    

    \item \textbf{The ``Intelligent Proctoring” Gap} 
        \begin{itemize}
            \item Another major research gap concerns the absence of mid-level intelligent proctoring systems. Existing literature illustrates a polarization between simple unproctored tools and costly AI-driven systems that require human oversight or aggressive live video analysis. \citet{Arno2021} demonstrated that only high-end commercial platforms provide comprehensive automation, yet these remain financially inaccessible to smaller universities. \citet{JiaHe2021} introduced an AI-based system integrating facial and voice analysis, but acknowledged privacy and scalability challenges stemming from continuous data transmission. \citet{TiongLee2021} proposed a deep-learning model for cheating detection, though it required GPU-intensive computation and complex setup. \citet{Rahim2020} observed that many institutions reverted to Google Forms and LMS quizzes precisely because proctoring tools were technologically demanding.
            \item These findings underline the lack of accessible “passive-AI” solutions—systems that ensure exam integrity through lightweight features such as tab-switch detection, periodic image capture, or local face verification without live video streaming. Developing such balanced systems would democratize secure assessments for low-resource educational institutions.
        \end{itemize}
    
    \item \textbf{The “Local Customization” Gap} 
        \begin{itemize}
            \item Reviewed studies also reveal a significant contextual and regulatory gap. Current online assessment technologies are predominantly developed for Western institutions and seldom consider local privacy laws, language interfaces, or administrative workflows relevant to African higher-education systems. \citet{Topuz2022} observed that nearly all systems in their global review were hosted abroad, while \citet{Kurniati2023} highlighted the difficulties of adapting foreign platforms to local socio-technical realities. \citet{UcaGunes2024} emphasized the absence of consistent institutional policies within emerging economies, resulting in reliance on externally governed software. Similarly, \citet{Tabassum2025} and \citet{Ali2025} stressed that assessments remain culturally and infrastructurally mismatched to learners’ environments.
            \item Consequently, there is little evidence of indigenous, region-specific assessment frameworks tailored to comply with national data-protection regulations, such as Ethiopia’s draft Personal Data Protection Proclamation, or aligned with local HR and university workflows. This presents an opportunity for Veritas Online Assessment to pioneer a locally hosted, policy-compliant, and culturally responsive assessment ecosystem.
        \end{itemize}
    
    
    \sloppy
    \item \textbf{ASAG(Automatic Short Answer Grading) Gaps} 
        \begin{itemize}
            \item Research on short answers remains narrow in application, as \citet{Schneider2024} identifies variability in GPT-4 performance, leading to inconsistent scoring for domain-specific and technical responses. Additionally, there are limitations in multilingual and non-English contexts.
        \end{itemize}
    
    
    \item \textbf{AES(Automatic Essay Scoring) Gaps}
        \begin{itemize}
            \item Human-LLM agreement is variable and often suboptimal, with \citet{Kundu2024} highlighting LLMs' tendency to be harsher on nuanced essays due to biases in training data; \citet{Mansour2024} and \citet{MizumotoEguchi2023} focus primarily on proficiency or linguistic traits, neglecting adaptation to non-English, technical domains and culturally diverse datasets, resulting in potential inequities for global users.
        \end{itemize}
    
\end{enumerate}

\subsection{Lessons Learned from Literature}

Three core insights arise:

\begin{enumerate}
    \item \textbf{Infrastructure and Inclusivity Matter}: \citet{Kurniati2023} and \citet{Ali2025} underscored the digital divide’s role in exam integrity, emphasizing flexible system design adaptable to varying connectivity conditions.
    \item \textbf{Future Assessments Must Be Ethical and Data-Conscious}: Recent works \citep{Kundu2024,Mansour2024,MizumotoEguchi2023} stress ethical implementation, transparent data handling, and user-centric approaches.
    \item \textbf{Integrity Cannot Rely on Trust Alone}: Research consistently shows that without technical methods, academic dishonesty is inevitable in remote settings. Teachers attempting to mitigate cheating by simply "changing question types" or "randomizing questions" found these methods insufficient without supervision. The system must proactively detect behaviors like tab-switching and multiple face detections \citep{Topuz2022,JiaHe2021,TiongLee2021}.
    \item \textbf{Infrastructure is the Primary Constraint}: The most frequent complaint in the literature regarding online exams is technical failure (internet failure, power outages). The Veritas architecture must be lightweight. Using client-side AI (processing behavior on the user's device rather than streaming heavy video to a server) is a crucial strategy to ensure the system works even with unstable connections \citep{Hussein2020,Ali2025,Topuz2022}.
    \item \textbf{User Experience Impacts Performance}: Complex interfaces increase student anxiety and technical error rates. Students are often unfamiliar with advanced online tools. The candidate portal must be intuitive and require minimal setup, ensuring the cognitive load is placed on the exam content, not the software interface \citep{Rahim2020,UcaGunes2024}.
    \item \textbf{Consistency}: LLMs provide reliable and generalizable scoring across large datasets, outperforming traditional methods in efficiency for AES and ASAG \citep{MizumotoEguchi2023,Schneider2024}.
    \item \textbf{Human-AI Collaboration}: Frameworks like dual-process models enhance accuracy and reduce errors, positioning LLMs as effective assistants rather than standalone tools in AES \citep{Xiao2024}.
    \item \textbf{Prompting Techniques}: Zero-shot and chain-of-thought prompting significantly improve rubric-based evaluation, enabling better handling of subjective criteria in both AES and ASAG \citep{MizumotoEguchi2023,Schneider2024}.
\end{enumerate}
