\section*{Acknowledgement}
\phantomsection
\addcontentsline{toc}{section}{Acknowledgement}

First and foremost, we express our deepest gratitude to the Almighty God for His endless grace, wisdom, and strength, which sustained us throughout the successful completion of this project. Without His guidance and blessings, this work would not have been possible.

We would like to sincerely thank all individuals and institutions who supported us during the development of our final year project entitled \textit{``Veritas: AI-Enhanced Online Assessment and Monitoring System.''}

Our heartfelt appreciation goes to our project advisor, Mr. Muleta Taye, for his invaluable guidance, constructive feedback, and continuous encouragement throughout the project lifecycle. His expertise in software engineering and dedication to academic excellence played a significant role in shaping both the technical direction and overall quality of this work.

We are also grateful to the faculty members of the Department of Software Engineering at Addis Ababa Science and Technology University for providing us with the academic foundation, technical knowledge, and supportive learning environment necessary to carry out this project. Special acknowledgment is extended to the Ministry of Innovation and Technology for its \textit{Digital Ethiopia 2030} initiative, which inspired our focus on local data sovereignty and technological independence.

Our sincere thanks are extended to the HR professionals, educators, and stakeholders who participated in interviews and surveys. Their practical insights and valuable feedback were instrumental in refining system requirements and addressing the specific challenges of the Ethiopian digital ecosystem.

We would also like to express our profound gratitude to our families and friends for their unwavering support, patience, and encouragement throughout the demanding phases of this project. Their belief in us served as a constant source of motivation during late nights and challenging moments.

Finally, we acknowledge the collective effort and collaboration of our team members—Abraham Mulugeta, Alazar Gebre, Tadiyos Dejene, Tamirat Dejene, and Yohannes Tigistu. Their teamwork, shared commitment, and mutual support were essential in bringing the Veritas system to completion.

This project would not have been possible without the combined support and contributions of everyone mentioned above. We are truly grateful to all.
