\singlespacing
\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{6pt}

% ==================================================
% Table 1: Enterprise Management and Multi-Tenancy Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Enterprise Management and Multi-Tenancy Requirements}
\label{tab:enterprise-mt} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-MT-001 & Multi-tenant architecture & The system shall completely isolate data, configurations, users, exams, and results between different enterprises/organizations. & Mandatory & Test / Inspection \\ \hline
FR-MT-002 & Enterprise registration & The system shall allow organizations to self-register with company details, contact person, and desired subscription plan. & Mandatory & Test \\ \hline
FR-MT-003 & Enterprise account approval & System administrator shall review and approve/reject enterprise registration requests. & Mandatory & Demonstration \\ \hline
FR-MT-004 & Enterprise profile management & Approved enterprises shall be able to update their profile, branding (logo, colors), and contact details. & Mandatory & Test \\ \hline
FR-MT-005 & Subscription tier enforcement & The system shall enforce feature restrictions based on the enterprise's subscription tier (Basic, Premium, Enterprise). & Mandatory & Test \\ \hline
FR-MT-006 & Tenant Deletion/Suspension & System administrator shall be able to suspend an enterprise account (locking out all associated users) and/or permanently delete an enterprise and all associated data after a 90-day retention period & Mandatory & Demonstration \\ \hline
\end{tabularx}

\vspace{2em}

% ==================================================
% Table 2: Authentication and User Management Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Authentication and User Management Requirements}
\label{tab:auth-requirements} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-AUTH-001 & Role-based access control & The system shall support roles: Super Admin, Enterprise Admin, Enterprise Staff, Candidate (temporary). & Mandatory & Test \\ \hline
FR-AUTH-002 & Enterprise-issued credential login & Candidates shall log in using enterprise-issued unique token or ID (no personal email/password required). & Mandatory & Test \\ \hline
FR-AUTH-003 & Enterprise admin/user management & Enterprise admins shall create/manage their staff accounts and permissions. & Mandatory & Test \\ \hline
FR-AUTH-004 & Face registration during exam onboarding & During exam start, candidates shall submit a live facial image that is stored as reference for the session. & Mandatory & Test \\ \hline
FR-AUTH-005 & Periodic face verification (Premium+) & The system shall periodically capture facial images during exam and compare with registration image using face recognition (available only for Premium/Enterprise plans). & Desirable & Test \\ \hline
FR-AUTH-006 & Session timeout \& re-authentication & Inactive sessions shall timeout after a configurable period and require re-authentication. & Mandatory & Test \\ \hline
\end{tabularx}

\vspace{3em}

% ==================================================
% Table 3: Examination Creation & Management Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Examination Creation \& Management Requirements}
\label{tab:exam-requirements} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-EXM-001 & Question Bank \& Metadata Management & Enterprise Admins shall create, categorize, and manage central question banks. The system must support the following question types: Multiple Choice (MCQ), True/False, Short Answer, and Essay. Each question must be assigned mandatory metadata for Topic/Category, Difficulty Level (e.g., Easy, Medium, Hard), and Media Support (allowing image, audio, or video attachments). & Mandatory & Test \\ \hline
FR-EXM-002 & Advanced Exam Configuration Wizard & The system shall provide a multi-step wizard to create exams with comprehensive settings: overall Exam Duration, Passing Score percentage, Negative Marking rules, and Targeted Randomization. Targeted Randomization must allow the Admin to define the exam structure by drawing N questions from specific categories or difficulty levels (e.g., 5 Easy questions from "Topic A," 10 Medium questions from "Topic B"). & Mandatory & Demonstration \\ \hline
FR-EXM-003 & Strict Scheduling \& Status Control & Admins shall precisely schedule exams with definite start date/time and end date/time, define available Invitation Methods (Email, Link, Token), and set the Maximum Allowed Participants. The system must automatically manage and display the exam's status lifecycle: Scheduled, Active, Closed, and Archived. & Mandatory & Test \\ \hline
FR-EXM-004 & Bulk Candidate Enrollment \& Credential Generation & Admins shall upload a CSV file or manually input candidate details. The system shall validate the uploaded data (e.g., checking for unique identifiers) and automatically generate unique, secure exam links or tokens for each candidate, sending the credentials via email. & Mandatory & Test \\ \hline
FR-EXM-005 & Exam Template Cloning \& Reuse & Admins shall be able to save any configured exam as a reusable template for future use. The system must also provide a Cloning function to duplicate all settings, question selections, and organization branding from any existing exam (Active or Closed) into a new, editable draft. & Mandatory & Demonstration \\ \hline
\end{tabularx}

\vspace{3em}

% ==================================================
% Table 4: Candidate Examination Interface Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Candidate Examination Interface Requirements}
\label{tab:candidate-exam-ui} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-CAND-001 & Secure Web Browser Mode \& Warning & The exam interface shall enforce full-screen mode and use JavaScript/browser APIs to disable right-click, copy-paste, and common browser shortcuts (e.g., Ctrl+C). A prominent, persistent warning banner shall inform the candidate that switching tabs/applications will be logged and may lead to disqualification. & Mandatory & Test \\ \hline
FR-CAND-002 & Server-Enforced Real-Time Timer & A strict countdown timer shall be displayed prominently. The remaining time shall be tracked and strictly enforced server-side to prevent client-side manipulation. The server shall reject answers submitted even milliseconds after the scheduled end time. & Mandatory & Test \\ \hline
FR-CAND-003 & Question Navigation \& Review & Candidates shall navigate questions sequentially or via a navigation index. They must be able to mark questions for review and receive a clear confirmation prompt before final submission or when time expires. & Mandatory & Demonstration \\ \hline
FR-CAND-004 & Auto-Save \& Submission Confirmation & Answers shall be auto-saved locally (using IndexedDB/LocalStorage) and synced to the server at least every 60 seconds. A comprehensive submission confirmation screen detailing the number of answered/unanswered questions must appear before final submission. & Mandatory & Test \\ \hline
FR-CAND-005 & Graceful Handling of Connectivity Issues & The system shall detect loss of connection and immediately queue answers locally using an offline-first approach (Service Workers/IndexedDB). When the connection restores, the system shall automatically and silently sync all queued data to the server and notify the candidate. & Mandatory & Test \\ \hline
FR-CAND-006 & Accessibility \& Readability Controls & The interface shall conform to at least WCAG 2.1 AA standards. Candidates shall have simple controls to adjust font size, color contrast (dark/light mode), and use standard keyboard navigation for accessibility. & Mandatory & Inspection \\ \hline
FR-CAND-007 & Secure Session Termination & If a major proctoring violation (e.g., identity mismatch (FR-PROC-004)) is flagged, the system shall provide the Enterprise Admin the option to force-terminate the candidate's session immediately. The candidate must receive a non-specific notification of termination. & Mandatory & Demonstration \\ \hline
\end{tabularx}

\vspace{3em}

% ==================================================
% Table 5: AI Proctoring & Monitoring Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{AI Proctoring \& Monitoring Requirements}
\label{tab:ai-proctoring} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-PROC-001 & Tab/window switch detection & The system shall detect and log every tab/window switch or application change during exam. & Mandatory & Test \\ \hline
FR-PROC-002 & Mouse activity monitoring & The system shall monitor mouse movement patterns and flag prolonged inactivity or unusual behavior. & Mandatory & Test \\ \hline
FR-PROC-003 & Webcam-based face detection & System shall continuously verify that a face is present in the webcam feed (Basic+ plans). & Mandatory & Test \\ \hline
FR-PROC-004 & Facial identity verification (Premium+) & The system shall periodically verify that the detected face matches the registered face (Premium/Enterprise only). & Desirable & Test \\ \hline
FR-PROC-005 & Multiple face detection & The system shall flag if more than one face is detected in the frame. & Desirable & Test \\ \hline
FR-PROC-006 & Proctoring event logging & All proctoring events shall be logged with timestamp, severity, and optional screenshot. & Mandatory & Inspection \\ \hline
FR-PROC-007 & Cheating probability score & The system shall calculate an overall cheating probability score based on all proctoring events. & Mandatory & Test \\ \hline
\end{tabularx}

\vspace{3em}

% ==================================================
% Table 6: Grading, Analytics & Certificate Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Grading, Analytics \& Certificate Requirements}
\label{tab:grading-analytics} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-GRAD-001 & Automatic grading for subjective/objective questions & The system shall automatically grade MCQ, True/False, fill-in-the-blank, short answer, and essay questions using configurable rubrics and AI assistance where applicable. & Mandatory & Test \\ \hline
FR-GRAD-002 & Blind grading & When a subjective answer is routed for mandatory human review (due to low AI confidence), the reviewer shall only see the candidate's response and the question rubric and must not see the candidate's name or any AI-assigned score until the manual grade is submitted. & Mandatory & Demonstration \\ \hline
FR-GRAD-003 & AI-assisted result analytics & The system shall provide detailed analytics including score distribution, time per question, cheating score impact, and rankings. & Mandatory & Demonstration \\ \hline
FR-GRAD-004 & Personalized feedback & Candidates shall receive personalized feedback reports including score, correct answers, detected cheating flags, and relative ranking. & Desirable & Demonstration \\ \hline
FR-GRAD-005 & Automatic certificate generation & The system shall generate and deliver customizable PDF certificates to passing candidates with organization branding and a QR code for verification. & Mandatory & Test \\ \hline
\end{tabularx}

\vspace{3em}

% ==================================================
% Table 7: Dashboard & Reporting Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Dashboard \& Reporting Requirements}
\label{tab:dashboard-reporting} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-DASH-001 & Role-Based Dashboards \& Customization & Super Admin, Enterprise Admin, and Staff shall have customized, widget-based dashboards showing relevant key metrics (KPIs) and quick links. Enterprise Admins shall be able to configure or reorder the widgets displayed on their dashboard. & Mandatory & Demonstration \\ \hline
FR-DASH-002 & Real-Time Exam Monitoring Dashboard & Enterprise Admins shall view live exams, active candidates, and proctoring flags in real-time. The dashboard shall feature low-latency updates (max 5-second latency) and color-coded severity indicators for proctoring events. & Mandatory & Demonstration / Test \\ \hline
FR-DASH-003 & Asynchronous Comprehensive Reporting & The system shall provide comprehensive reports for exam results, proctoring logs, and candidate performance. For reports exceeding 500 records, generation shall be asynchronous (user is notified via email/in-app when the report is ready). & Mandatory & Test \\ \hline
FR-DASH-004 & Granular Data Export Formats & Reports shall be exportable in multiple formats: PDF (formatted, summary), Excel/CSV (raw data for analysis), and JSON/API endpoint (for integration with Enterprise BI tools - Enterprise-tier feature). & Mandatory & Test \\ \hline
FR-DASH-005 & Audit Log \& Activity Tracking & Super Admins and Enterprise Admins shall have a dedicated report/dashboard to view a complete, immutable audit trail of all critical actions (e.g., user creation, exam changes, deletion, payment history) with timestamp and actor details. & Mandatory & Inspection \\ \hline
FR-DASH-006 & Performance \& Trend Analytics & Enterprise Admins shall access analytics dashboards to track historical trends (e.g., month-over-month exam volume, average scores over time) and view performance benchmarks against other Enterprise exams (anonymously). & Desirable & Demonstration \\ \hline
FR-DASH-007 & Custom Report Builder & The system shall provide an interface that allows Enterprise Admins to define and save custom reports by selecting specific filters, fields, and grouping criteria (e.g., performance by department/location). & Desirable & Demonstration \\ \hline
\end{tabularx}

\vspace{3em}

% ==================================================
% Table 8: Payment & Subscription Requirements
% ==================================================
\begin{tabularx}{\linewidth}{|l|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}X|l|l|}
\caption{Payment \& Subscription Requirements}
\label{tab:payment-subscription} \\ \hline
\textbf{Req. ID} & \textbf{Requirement Title} & \textbf{Description} & \textbf{Priority} & \textbf{VM} \\ \hline
FR-PAY-001 & Gateway Integration \& Localization & The system shall integrate with the specified Ethiopian payment gateways (Telebirr, CBE Birr) and support local currency (ETB) transactions. & Mandatory & Test \\ \hline
FR-PAY-002 & Secure Transaction Handling & The system shall comply with PCI DSS Level 2 (or equivalent standard for handling payment tokens/data) and ensure all payment data transmission is encrypted using TLS 1.2 or higher. & Mandatory & Inspection / Audit \\ \hline
FR-PAY-003 & Subscription Plan Management & Super Admin shall define, modify, activate, and deactivate subscription plans, including features, usage limits (max users, max exams), and pricing structures. & Mandatory & Demonstration \\ \hline
FR-PAY-004 & Automatic Recurring Billing \& Dunning & The system shall automatically handle recurring billing and renewal. It must implement a dunning process to manage failed payments, including retries and automated notification of the Enterprise Admin. & Mandatory & Test \\ \hline
FR-PAY-005 & Upgrade/Downgrade Management & The system shall allow Enterprise Admins to upgrade or downgrade their subscription plan, with proration calculated and applied automatically for the remaining period of the current billing cycle. & Mandatory & Test \\ \hline
FR-PAY-006 & Invoice \& Tax Compliance & The system shall automatically generate and deliver a detailed, legally compliant invoice (including applicable Ethiopian taxes or VAT) upon every payment or billing event (new subscription, renewal, proration). & Mandatory & Test / Demonstration \\ \hline
FR-PAY-007 & Billing History \& Management & Enterprise Admins shall have a dedicated portal to view their complete billing history, download all past invoices (FR-PAY-006), and update their payment methods. & Mandatory & Demonstration \\ \hline
FR-PAY-008 & Account Suspension Workflow & In the event of persistent payment failure (after the dunning process), the system shall automatically trigger the suspension of the Enterprise account, notifying the Enterprise Admin 48 hours prior to the action. & Mandatory & Demonstration \\ \hline
\end{tabularx}
